Death By Dropdown?

### 2025-04-09 conference-materials/2025_shiny-conf/slides.qmd
Enhances framing effect explanations in slides
- Refines slide content to clarify psychological principles of framing, illustrating the impact of progress vs. gap framing.

- This illustrates the powerful psychological principles at work...we're showing identical data but creating completely different mental states
- Progress framing highlights achievement and builds confidence...marketing team preferred this approach
- Gap framing creates urgency and focuses on improvements needed - product teams used this view
- "This isn't just theory - a classic study showed that people react completely differently when presenting identical medical treatment outcomes as either a 90% survival rate or a 10% mortality rate ... even though it's the same data"
- Consider how framing in your dashboards might drive different decisions
:::

>>>>

- This illustrates powerful psychological principles in action...we're showing identical underlying data but creating completely different mental states [CLICK]
- In this example, progress (gain) framing shows the *relative difference* between the raw value and the benchmark...highlighting achievement and building confidence
  * SoundPulse's marketing team preferred this approach for stakeholder presentations and showing the progress made [CLICK]
- BUT...the gap (loss) framing shows the raw values vs. the benchmark...creating urgency and focusing on improvements needed 
  * Their product teams used this view to prioritize development
- This isn't just theory - classic research shows people react completely differently to identical medical outcomes presented as either a "90% survival rate" or a "10% mortality rate"
- Think about your own dashboards - how might framing choices drive different decisions for your users?
:::
